---
title: "Assignment4"
author: "Will Holt"
date: "September 26, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Questions
####1. FiveThirtyEight Data (30 points): Navigate on GitHub to https://github.com/rudeboybert/fivethirtyeight and read README.md. Seriously, it will include everything you need.

#####a. Install the fivethirtyeight package.
```{r}
#Install the package
#install.packages(fivethirtyeight)
#Access the package
library(fivethirtyeight)
```

#####b. In the listing of Data sets in package fivethirtyeight,assign the eighteenth data set to an object
```{r}
#df <- fivethirtyeight::college_recent_grads
```

#####c. Use a more detailed list of the data sets to write out the URL in a comment to the related news story

```{r}
#Follow these instructions to find the 18th dataset within the FiveThirtyEight dataset:
#Use the code vignette("fivethirtyeight", package = "fivethirtyeight")
#Scroll down to the college_grad_students dataset and then scroll right to the URL
#The URL is http://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/
```


#####d. Using R command(s), give the dimensions and column names of this data frame.

```{r}
#Identify the dimensions of the college_recent_grads dataset
dim(college_recent_grads)

#Identify the Column Names of the college_recent_grads dataset
colnames(college_recent_grads)
```


####2. Data Summary (30 points): Use your newly assigned data frame for Question 2.

#####a. Write an R command that gives you the column names of the data frame. Right after that, write one that counts the number of columns but not rows. Hint: The number hould match one of your numbers in Question 1d for dimensions.
```{r}
colnames(college_recent_grads)
ncol(college_recent_grads)
```

#####b. Generate a count of each unique major_category in the data frame. I recommend using libraries to help. To be clear, this should look like a matrix or data frame containing the major_category and the frequency it occurs in the dataset. Assign it to major_count.

```{r}
Major_Category <- as.data.frame(table(college_recent_grads$major_category))
library(plyr)
rename (Major_Category, c("Var1" = "Major", "Freq" = "Major_Count"))
#After this code is run, return to FiveThirtyEight
library(fivethirtyeight)
```


#####c. To make things easier to read, put par(las=2) before your plot to make the text perpendicular to the axis. Make a barplot of major_count. Make sure to label the title with something informative (check the vignette if you need), label the x and y axis, and make it any color other than grey. Assign the major_category labels to their respective bar. Flip the barplot horizontally so that bars extend to the right, not upward. All of these options can be done in a single pass of barplot(). Note: It is okay if it is wider than the preview pane.

```{r}
Major_Category <- as.vector(table(college_recent_grads$major_category))
#Check Class
class(Major_Category)
#Create Labels for barplot and then create plot:
Major_Names <- c("Agriculture & Natural Resources", "Arts", "Biology & Life Science", "Business", "Communications & Journalism", "Computers & Mathematics", "Education", "Engineering", "Health", "Humanities & Liberal Arts", "Industrial Arts & Consumer Services", "Interdisciplinary", "Law & Public Policy", "Physical Sciences", "Psychology & Social Work", "Social Science")
par(las=2, barplot(Major_Category, horiz = T, names.arg = Major_Names, col = "green"))
```

#####d. Write the fivethirtyeight data to a csv file. Make sure that it does not have row labels.

```{r}
Major_Category.csv <- as.data.frame(table(college_recent_grads$major_category))
rownames(Major_Category.csv) <- c()
colnames(Major_Category.csv) <- c("Var1" = "Major", "Freq" = "MajorCount")
write.csv(Major_Category.csv)
```

#link to GitHub
https://github.com/WillHolt-SMU/DataScienceHW
